Automated Topic Naming

### 2011-08-23 ese/ese.tex
before line-shortening

\begin{abstract}
% %\todo[inline]{Topics and LDA sooner, Topics/concept location is a known
Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on two large-scale RDBMS projects: MySQL and MaxDB.  The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent dirichlet allocation \and Topic models}

@@

\item provides a method of cross-project analysis via topic labelling; and
 applies these techniques to visualize NFRs over time, and to analyze maintenance activities.
\end{itemize}

>>>>

\begin{abstract}
% %\todo[inline]{Topics and LDA sooner, Topics/concept location is a known
Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale RDBMS projects: MySQL, PostgreSQL and MaxDB.  The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent dirichlet allocation \and Topic models}

@@

\item examines how NFRs correlate with the work of individual developers;
\item provides a method of cross-project analysis via topic labelling; and
 applies these techniques to visualize NFRs over time, and to analyze maintenance activities.

\end{itemize}
